US General Society Survey Analysis

### 2024-03-16 paper/paper.qmd
added the weakness and stuff

# Models

@@

# Results

@@

Weaknesses and next steps should also be included.

>>>>

# Models/Results

@@

@@

  It is near impossible to have data sets that are completely error-free and the same is true for this data-set. The data-set we used as analysis does not take into account the opinions of non-citizens and who they would have voted for. A lot of marginalized opinions are being left out when we clean the data and we only look for people that could vote. For example refugees may have a different opinion on who got elected in the 2020 presidential candidate as they come from a different aspect of life and have different priorities that need to be addressed such as housing and or health care. 
  Another weakness in our data-set is what occurs with a lot of data-sets, which is missing values. This data set also contained them and those needed to be cleaned so that our analysis would not sway. Speaking of missing values, insignificant values were ignored in some of the models as well. For, example some of the presidential candidates got so little votes that including them would have actually hindered our ability to see the trends so we had to group them in others. This was beneficial for this paper but  if we do indeed continue to analyse this paper for other purposes, this might cause problems.

  In terms of next steps for this paper, we look forward to predict the 2024 election results by comparing the what the general priorities of the population is. We could look at population by immigration status, gender, age, or their previous 2020 voting results.  If we are able to correctly predict the results based on the model continuously, it would help understand the priorities of american citizens; knowledge that would in turn help us help them.
